---
title: "NFL Prediction: Analysis of Passing EPA based on first nine weeks"
author: 
  - Hyungsoo Park
thanks: "https://github.com/kakaomonk/nfl-prediction"
date: today
date-format: long
abstract: "This paper focuses on the later Passing EPA in 2023 NFL based on the first weeks league data."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
```

# Introduction

This paper explores the total expected points added on passing for quarterback position players. The quarterback position is a role that passes to a receiver from an offensive lineman and passes the ball to a running back, which means the quarterback position plays an essential role in winning a football game. In addition, a team without good quarterback players has less chance to win the football games in a league.

Therefore, the total expected points added on passing for quarterback players is one of the most important factors in evaluating each quarterback player. This study focuses on the correlation between "passing_epa" and other related factors in the football game.

The data from the first nine weeks of the 2023 NFL season were used to predict the later 2023 season's total expected points added on passing.

In the following section, @sec-data explains the data used and the cleaning process, and @sec-model analyzes the built model for this study.

# Data {#sec-data}

The raw data used was retrieved from NFLverse[@citeNflverse]. The data was cleaned by R[@citeR] and Tidyverse[@citeTidyverse], and analyzed by r. The raw data from @citeNflverse contains all data from 1999. The cleaned data contains only player data in the first 9 weeks of 2023. The variables in interest are 'passing_epa', 'player_id', 'season', 'week', 'completions', 'attempts', 'passing_yards', 'passing_tds', 'interceptions', 'sacks', and 'sack_yards'.

```{r}
#| label: tbl-cleaned
#| tbl-cap: Cleaned NFL data
#| echo: false
#| warning: false

library(here)
analysis_data <- read_csv(here("data/analysis_data/analysis_data.csv"))
analysis_data
```

# Model {#sec-model}

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

```{=tex}
\begin{align} 
y &= B_0 + B_{1} X_{completions} + B_{2} X_{attempts} + B_{3} X_{passing_yards} \\
&+ B_{4} X_{passing_tds} + B_{5} X_{interceptions} + B_{6} X_{sacks} + B_{7} X_{sack_yard}
\end{align}
```
The model was ran in R[@citeR] by using rstanarm[@rstanarm].

### Model justification

The model considers 6 predictor variables (completions, attempts, passing_yards, passing_tds, interceptions, sacks, sack_yard) to predict passing_epa.

# Results

The results from the model is in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_9_weeks_passing_model_2023 <-
  readRDS(file = here::here("models/first_9_weeks_passing_model_2023.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

first_9_weeks_passing_model_2023
```

As a result, the paper could predict that the passing distance (passing_yards) and the number of touchdowns influence to the total expected points added on passing.

\newpage

# References
